---
title: "mulinkr"
author:
    - name: Léopold Guyot
output:
    BiocStyle::html_document:
        self_contained: yes
        toc: true
        toc_float: true
        toc_depth: 2
        code_folding: show
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('mulinkr')`"
vignette: >
  %\VignetteIndexEntry{mulinkr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
```

The `mulinkr` package writes `QFeatures` objects and their assay links to `.h5mu`
files and reads them back into R.

Here we will use the example data `feat3` from `QFeatures`.

```{r load-data}
library(mulinkr)
data("feat3", package = "QFeatures")
feat3
```

We first prepare the object for writing. This makes feature names unique across
assays when needed and converts date columns to character.

```{r prepare}
preparedFeat3 <- prepareQFeatures(feat3)
```

Then we write the prepared object to a temporary `.h5mu` file.

```{r write}
filePath <- tempfile(fileext = ".h5mu")
writeLinkH5MU(preparedFeat3, filePath)
```
The created `.h5mu` file can then be used in python or in R.

In python, the file can be read as a [`mulink` object](https://mulink.readthedocs.io/). 

```python
import mudata as md
import mulink

mdata = md.read_h5mu("yourFile.h5mu")

print(mdata)
```
In R, the object can be reimported back as a `QFeatures` object.

```{r read}
newQFeatures <- readLinkH5MU(filePath)
newQFeatures
```

```{r cleanup, include=FALSE}
unlink(filePath)
```

```{r sessionInfo}
sessionInfo()
```
